Transfer Learning in Multimodal Compositional and Relational Reasoning:\\Supplementary Material

### 2019-11-15 cvpr_submission/introduction.tex
transfer learning para

How to acutely employ transfer learning in the case of multi-modal tasks~\cite{mogadala2019trends}, which combine both modalities mentioned above, i.e., vision and language, is another engaging research question. While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, there is no obvious approach to combine both and hope to perform well on, say, Visual Question Answering. New models and mechanisms, such as attention~\cite{bahdanau2014neural}, are appropriate to handle the intricate relations between two (or more) modalities.

\paragraph{Contributions}
The contributions of this work are as follows.
\begin{itemize}
	\compresslist
	\item We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
	\item We propose a taxonomy of transfer learning, inspired from~\cite{pan2009survey}, applied to the domain of visual reasoning. Articulated around 3 main axes, we illustrate it through the COG dataset, as well as the CLEVR~\cite{johnson2017clevr} diagnostic dataset for Image QA.
	\item Following, we measure the impact of transferring the whole pretrained SAMNet model in the 3 proposed transfer learning settings: feature transfer, temporal transfer and reasoning transfer. This analysis is supported by an extensive set of experiments using the COG and CLEVR datasets, as well as their variants. Several of these experiments show the significant generalization capabilities of SAMNet.
\end{itemize}

>>>>

In this work, we focus on multi-modal learning~\cite{mogadala2019trends} combining vision and language,
and in particular, transfer learning for visual reasoning tasks with a rich logical structure, e.g., see~\cite{johnson2017clevr,yang2018dataset}. 
While models such as BERT and ResNet can be transferred efficiently in the same modality they were pretrained on, challenges arise
once the modalities have been fused.
For example, in compositional reasoning problems that involve objects with multiple attributes,
feature representations in the source domain may be entangled and not easily transfer over to the target domain~\cite{johnson2017clevr}.
In video reasoning, an additional challenge in the temporal dimension is whether a model that is trained on shorter video sequences will 
transfer over to longer sequences~\cite{yang2018dataset,song2018explore}.
To address these challenges, mechanisms such as attention~\cite{bahdanau2014neural} 
and external memory~\cite{graves2014neural, graves2016hybrid,weston2014memory} 
which facilitate higher-level abstractions, seem more promising.

Our main contributions are:
\begin{itemize}
	\compresslist
	\item We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
	\item We propose a taxonomy of transfer learning, inspired from~\cite{pan2009survey}, applied to the domain of visual reasoning. Articulated around 3 main axes, we illustrate it through the COG dataset, as well as the CLEVR~\cite{johnson2017clevr} diagnostic dataset for Image QA.
	\item Following, we measure the impact of transferring the whole pretrained SAMNet model in the 3 proposed transfer learning settings: feature transfer, temporal transfer and reasoning transfer. This analysis is supported by an extensive set of experiments using the COG and CLEVR datasets, as well as their variants. Several of these experiments show the significant generalization capabilities of SAMNet.
\end{itemize}
